Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
paper changes

% \begin{abstract}
% This is the paper's abstract \ldots
% \end{abstract}

@@

>>>>

@@

\section{Data}
As with any learning algorithm we require to have some data available.  We use Apple's iPhone and xSensor application to record, train and test our various algorithms.  For each training example for any gesture type xSensor returns to us an ordered series of vectors in $\mathbb{R}^n$ containing instantaneous acceleration and gyroscope data sampled at 32 hz.  For the most part we normalize each training example by scaling each vector in the training example by $\frac{n}{\sum_n{\parallel x_n \parallel}}$, where the training example consists of $n$ instantaneous feature vectors.
